### 2021-05-05 newvariant.tex
adding one more sentence and funding

Using the Gamma-approximation framework \citep{doi:10.1098/rsif.2020.0144} can help us reconcile different estimates more clearly.
For example, \cite{davies2021estimated} estimated a relative strength of $\rho=1.77$ assuming a fixed generation generation interval at 5.5 days from $\delta=0.104\pday$ in one of their regression analysis.
Similarly, \cite{volz2021transmission} estimated $\rho=1.79$ by directly comparing the ratio between $\Rv$ and $\Rw$ assuming a mean generation interval of 6.5 days and a squared coefficient of variation of 0.38.
In this case, the latter study's longer mean generation interval (which increases $\rho$) is counter-balanced by the effects of their wider distribution (which decreases $\rho$); calculations using our approximation framework produce qualitatively similar results ($\rho=1.81$ from $\Gw=\Gv=6.4\days$, $\kappa=0.38$, $\delta=0.104\pday$, and $\rw=0\pday$).
If we consider short and wide generation interval estimates from Tianjin, China ($\Gw=\Gv=2.57\days$ and $\kappa=1$; \cite{ganyani2020estimating}), we obtain $\rho=1.27$ (from $\delta=0.104\pday$ and $\rw = 0\pday$).
Although these estimates are more consistent with the attack rate analysis \citep{ukinvest},
we do not claim that our estimates of $\rho$ are more accurate.
This calculation simply highlights the importance of propagating uncertainty in generation-interval distributions in assessing the relative strength and speed of SARS-CoV-2 variants.

@@

B.M.B. was supported by the Natural Sciences and Engineering Research Council of Canada. 
J.D. was supported by the Canadian Institutes of Health Research, 
the Natural Sciences and Engineering Research Council of Canada, 
and the Michael G. DeGroote Institute for Infectious Disease Research.
J.S.W. was supported by the National Science Foundation (2032082).
The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.

>>>>

Using the Gamma-approximation framework \citep{doi:10.1098/rsif.2020.0144} can help us reconcile different estimates more clearly.
For example, \cite{davies2021estimated} estimated a relative strength of $\rho=1.77$ assuming a fixed generation generation interval at 5.5 days from $\delta=0.104\pday$ in one of their regression analysis.
Similarly, \cite{volz2021transmission} estimated $\rho=1.79$ by directly comparing the ratio between $\Rv$ and $\Rw$ assuming a mean generation interval of 6.5 days and a squared coefficient of variation of 0.38.
In this case, the latter study's longer mean generation interval (which increases $\rho$) is counter-balanced by the effects of their wider distribution (which decreases $\rho$); calculations using our approximation framework produce qualitatively similar results ($\rho=1.81$ from $\Gw=\Gv=6.4\days$, $\kappa=0.38$, $\delta=0.104\pday$, and $\rw=0\pday$).
If we consider short and wide generation interval estimates from Tianjin, China ($\Gw=\Gv=2.57\days$ and $\kappa=1$; \cite{ganyani2020estimating}), we obtain $\rho=1.27$ (from $\delta=0.104\pday$ and $\rw = 0\pday$).
Although these estimates are more consistent with the attack rate analysis \citep{ukinvest},
we do not claim that they are more accurate---
in particular, contact tracing data can be biased towards particular types of contacts that are easily identified such as household contacts, which could also affect the estimate of $\rho$.
Instead, this calculation simply highlights the importance of propagating uncertainty in generation-interval distributions in assessing the relative strength and speed of SARS-CoV-2 variants.

@@

B.M.B. was supported by the Natural Sciences and Engineering Research Council of Canada. 
J.D. was supported by the Canadian Institutes of Health Research, 
the Natural Sciences and Engineering Research Council of Canada, 
and the Michael G. DeGroote Institute for Infectious Disease Research.
J.S.W. was supported by the National Science Foundation (2032082).
S.F. was supported by the Wellcome Trust (210758/Z/18/Z).
The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
